Community-Conditioned Language Models

### 2020-11-20 paper/paper.tex
cleanup

However, we want to measure the ability of the LMCC to correctly
recognize messages coming from a given community $c_j$. We could use
something like an F-score, but we prefer to use the entropy metric,
which is has stronger information-theoretic grounds, and is a measure
of the uncertainty of the LMCC, given messages from a particular 
community. 
Technically, the linguistic indiscernibility of community $c_j$ is defined 
as the exponential of the entropy of the $j$ row in \(C\),
which is a probability distribution 
of predicted community for a random message from $c_j$.
In sum, we have the formula: \bn{Took out $D$. is it needed elsewhere?}
\[\Ind_j = e^{-\sum_i C_{ij} log(C_{ij})}\]

Indiscernibility is a robust measure: it is almost perfectly
correlated for various CCLM (transformer, LSTM and various $c$) $M$.
In fact, we observe a correlation between the indiscernibility 
measures by every pair of models with Pearson's r $\geq 0.98$ 
and $p < 0.0001$ (see, for example, \cref{fig:lmcc_ppl}).

@@

\jp{We could also compute the entropy of rows of Cij = snap cosine similarity w/ softmax.}

>>>>

However, we want to measure the ability of the LMCC to correctly
recognize messages coming from a given community $c_j$. We could use
something like an F-score, but we prefer to use a perplexity-like metric,
which is has stronger information-theoretic grounds.
We define the linguistic indiscernibility of community $c_j$, noted $\Ind_j$, 
as the exponential of the entropy of the $j$th row in \(C\),
(which is a probability distribution
of predicted community for a random message from $c_j$):
\[\Ind_j = e^{-\sum_i C_{ij} log(C_{ij})}\]
Intuititely, $\Ind_j$ is a measure of the uncertainty of the LMCC,
given messages from a community $c_j$.

Indiscernibility of a given community is a robust measure: it is
almost perfectly correlated across CCLMs (such as transformers, LSTM
and various values of $l_c$).  In fact, we observe a correlation
between the indiscernibility measures by every pair of models with
Pearson's $r \geq 0.98$ and $p < 0.0001$ (see, for example,
\cref{fig:lmcc_ppl}).

@@

% We could also check if communities are well-separated in the SNAP community encodings
